A pipeline to analyse time-course gene expression data

### 2019-07-27 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\begin{verbatim}
##   
   checking for file '/tmp/RtmpHrqs5v/remotes341f57a29b/NelleV-moanin-205e154/DESCRIPTION' ...

v  checking for file '/tmp/RtmpHrqs5v/remotes341f57a29b/NelleV-moanin-205e154/DESCRIPTION'
##

@@

\begin{itemize}
\item
  \texttt{biocLite} is no longer the recommended way to install bioconductor. Instead
  \texttt{BiocManager::install(c("edge",\ "NMI"))}. But this is dependent on
  bioconductor/R version. Also, now that docker, can you change the
  installation to just be simple one-liner (and \texttt{BiocManager::install} can
  also do non-bioc packages, and is much more reliable.)
\item
  I get multiple errors in compilation of file. Not sure, however, why
  TravisCI didn't hit these problems, so you might want to see what's going on
  there. Probably caching or something, so might want to occassionally remove
  the cache and run again, if TravisCI is saving the cache. One error I fixed,
  but wasn't sure about this error (changed it to \texttt{entrezgene\_id} and seems to
  be running now\ldots{}):
\end{itemize}

@@

\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\hline
  & Pathway & Percentage & Adj. p-value\\
\hline
05169 & Epstein-Barr virus infection & 37 & 0\\
\hline
04060 & Cytokine-cytokine receptor interaction & 31 & 0\\
\hline
04668 & TNF signaling pathway & 45 & 0\\
\hline
05164 & Influenza A & 38 & 0\\
\hline
04621 & NOD-like receptor signaling pathway & 34 & 0\\
\hline
05162 & Measles & 37 & 0\\
\hline
04630 & JAK-STAT signaling pathway & 33 & 0\\
\hline
05160 & Hepatitis C & 34 & 0\\
\hline
04620 & Toll-like receptor signaling pathway & 40 & 0\\
\hline
05167 & Kaposi sarcoma-associated herpesvirus infection & 29 & 0\\
\hline
\end{tabu}

>>>>

\begin{verbatim}
##   
   checking for file '/tmp/RtmpLM5IuQ/remotes347f085d5d/NelleV-moanin-205e154/DESCRIPTION' ...

v  checking for file '/tmp/RtmpLM5IuQ/remotes347f085d5d/NelleV-moanin-205e154/DESCRIPTION'
##

@@

\begin{itemize}
\tightlist
\item
  \texttt{biocLite} is no longer the recommended way to install bioconductor. Instead
  \texttt{BiocManager::install(c("edge",\ "NMI"))}. But this is dependent on
  bioconductor/R version. Also, now that docker, can you change the
  installation to just be simple one-liner (and \texttt{BiocManager::install} can
  also do non-bioc packages, and is much more reliable.)
\end{itemize}

@@

\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\hline
  & Pathway & Percentage & Adj. p-value\\
\hline
05169 & Epstein-Barr virus infection & 37 & 0\\
\hline
04060 & Cytokine-cytokine receptor interaction & 31 & 0\\
\hline
04668 & TNF signaling pathway & 45 & 0\\
\hline
05164 & Influenza A & 38 & 0\\
\hline
04621 & NOD-like receptor signaling pathway & 34 & 0\\
\hline
05162 & Measles & 37 & 0\\
\hline
04630 & JAK-STAT signaling pathway & 33 & 0\\
\hline
05160 & Hepatitis C & 34 & 0\\
\hline
04064 & NF-kappa B signaling pathway & 39 & 0\\
\hline
04620 & Toll-like receptor signaling pathway & 40 & 0\\
\hline
\end{tabu}
